# Data Preprocessing
This file is used to clean the dataset for later data analysis and predictive model

## Load Libraries
```{r}
library(httr)
library(jsonlite)
library(DBI)
library(RSQLite)
library(ggplot2)
```


## Check NAs
### Create "check missing" function

```{r}

check_missing <- function(thedata) {
  # Total number of rows
  n_rows <- nrow(thedata)
  
  # Find missing percentage for each column
  missing_summary <- sapply(thedata, function(x) sum(is.na(x)) / n_rows * 100)
  
  # Turn into a nice data frame
  missing_df <- data.frame(
    column = names(missing_summary),
    missing_percent = round(missing_summary, 2)  # Round to 2 decimal places
  )
  
  # Sort by missing_percent descending
  missing_df <- missing_df[order(-missing_df$missing_percent), ]
  
  print(missing_df)
  
  # Missing value graph for the report
  ggplot(missing_df, aes(x = reorder(column, missing_percent), y = missing_percent, fill = -missing_percent)) +
      geom_bar(stat = "identity") +
      geom_text(aes(label = paste0(round(missing_percent, 1), "%")), 
                hjust = -0.1,  # Move the label a little to the right of bar
                size = 4) +    # Text size
      coord_flip() +
      labs(x = "Attribute", y = "Missing Data (%)", title = "Percent Missing of each Attribute in Jikan Anime Data", fill = "Missing Percent" ) +
      theme_minimal() +
      theme(plot.title = element_text(hjust = 0.5, size = 28, face = "bold"),
            axis.title.x = element_text(size = 19),
            axis.title.y = element_text(size = 19),
            axis.text.y = element_text(size = 14),)
  
}


```

### check current raw dataset

```{r}
# Connect if not already
conn <- dbConnect(SQLite(), "anime_full_database.sqlite")

# Read the table
anime_data0 <- dbReadTable(conn, "anime_full")

check_missing(anime_data0)


```

When title is missing, the entire row is invalid, we remove rows with title missing

```{r}

# Keep only rows where title is NOT missing
anime_data1 <- anime_data0[!is.na(anime_data0$title), ]
sum(is.na(anime_data1$title))
nrow(anime_data1)

```

The valid anime rows is now 28318 instead of 28477. Inspect missing values again:

```{r}
check_missing(anime_data1)
```

# Clean Data for Predictive Analysis

#### we remove rows that don't have genre appear

#### we remove rows that don't have producers

#### we remove rows that don't have studios

and check missing data again

```{r}
anime_data2 <- anime_data1[!is.na(anime_data1$genres),]
nrow(anime_data2)
check_missing(anime_data2)
anime_data3 <- anime_data2[!is.na(anime_data2$producers),]
anime_data4 <- anime_data3[!is.na(anime_data3$studios),]
check_missing(anime_data4)

```

#### Then, we select only the attributes we want

```{r}
selected_attributes <- c("mal_id", "title", "type", "episodes", "status", 
                          "rating", "score", "scored_by", "rank", "popularity", 
                          "members", "favorites", "genres", "studios", "producers")
anime_data5 <- anime_data4[, selected_attributes]

```

### Last

Use the dataset you want for each analysis section:\\

-   anime_data0 = raw data from Jikan API

-   anime_data1 = anime data with no empty title

-   anime_data2 = anime data with no empty title and no empty genres

-   anime_data5 = anime data with no empty title, no empty genres, no empty producers, no empty studios, and reduced columns.

### Improvement if have time

instead of make a copy of each cleaned dataset, an efficient way can be implemented to make it save more storage space

For studios, a manual clean can be implemented since some of the studios with 1-3 anime counts are basically a sub-department from a large studio. We would need to change their categorical value into the name of their large studio. Some other studios with 1-3 anime counts are because the collboration of couple studios together.

### Free block: test/see the data frame here

Type the name of data frame to see the who dataset Type the str(name of dataframe to see the structure of it)

```{r}
anime_data5
str(anime_data5)
```
