# Data Preprocessing for Predictive Model Part 2: Grouping and New Attributes

## Load libraries

```{r}
library(dplyr)
library(tidyr)
library(stringr)
library(httr)
library(jsonlite)
library(DBI)
library(RSQLite)
library(ggplot2)
```

#### Studios data processing

The data analysis for studios is in data_analysis.Rmd. We want to include the studios column when training the predictive model. Since the column has too many unique values, doint the one-hot encoding will result in a very high dimension of our dataset. We have considered to choose the top10 studios with higest 10 average score, but the output result shows studios with only 1 to 3 anime counts, which does not represent the studios' performance enough.

Based on the analysis, some of the well-known/popular studios usually have a high count of anime with along with a high score. Therefore, we decide to choose studios that have anime count \>= 30 with a score \>= 7.03 (the top 25% of the score).

##### find anime count for each studios

```{r}
studios_stats <- anime_data5 |>
  group_by(studios) |>
  summarise(
    count = n(),
    avg_score = mean(score, na.rm = TRUE),
    .groups = "drop"
  )
studios_stats
```

##### Filter studios with count \>= 30 and score \>= 7.03

The output tibble show the studios that satisfy with our criteria. The output makes sense because these studios below are all well-know studios that produce popular anime each season.

```{r}
top_studios <- studios_stats |>
  filter(count >= 30, avg_score >= 7.03)
top_studios
```

##### Add, Delete column for studios

22 studios were selected. However, 22 is still too much for one-hot encoding. As the result, we decide to further manipulate the column by adding a new column with the following description: For each row, if the studio belongs to 1 of the 22 top studios, we classify it as "top" Otherwise, it is "other".

```{r}
# list of top studios
top22_studios <-  top_studios$studios
# create a copy of anime data
anime_data6 <-anime_data5
anime_data6$studio_rank <- ifelse(
  anime_data6$studios %in% top22_studios,
  "Top",
  "Other"
)
anime_data6$studio_rank <- factor(anime_data6$studio_rank, levels = c("Top", "Other"))

# delete studios column
anime_data6 <- anime_data6 |> select(-studios)
anime_data6
```

Examine the dataset:

```{r}
boxplot(score ~ studio_rank,
        data = anime_data6,
        main = "Score Distribution: Top vs Other Studios",
        xlab = "Studio Rank",
        ylab = "Anime Score",
        col = c("lightblue", "lightgreen"))
```

##### Producers

###### Filter the top producers

```{r}
top_producers <- producer_stats |>
  filter(count >= 30, avg_score >= 7.03) |>
  arrange(desc(avg_score))

top_producers
```

###### Add column to classify producer as "top" or "other"

```{r}

top_producer_list <- top_producers$producer

tag_producer_rank <- function(producer_string) {
  if (is.na(producer_string)) return("Other")
  individual_producers <- str_split(producer_string, ",\\s*")[[1]]
  if (any(individual_producers %in% top_producer_list)) {
    return("Top")
  }
  return("Other")
}

anime_data6$producer_rank <- sapply(anime_data6$producers, tag_producer_rank)

anime_data6$producer_rank <- factor(anime_data6$producer_rank, levels = c("Top", "Other"))
# delete producers column
anime_data6 <- anime_data6 |> select(-producers)
anime_data6
```

###### Examin new dataset

```{r}

boxplot(score ~ studio_rank,
        data = anime_data6,
        main = "Score Distribution: Top vs Other Producers",
        xlab = "Producer Rank",
        ylab = "Anime Score",
        col = c("lightblue", "lightgreen"))
```

#### Type Data Processing

```{r}
anime_data7 <- anime_data6
anime_data7$type_rank <- case_when(
  anime_data7$type %in% c("Movie", "TV") ~ "High",
  anime_data7$type %in% c("TV Special", "Special", "ONA") ~ "Mid",
  anime_data7$type %in% c("OVA", "Music", "CM", "PV") ~ "Low",
  TRUE ~ "Other"
)

anime_data7$type_rank <- factor(anime_data7$type_rank, levels = c("Low", "Mid", "High"))
anime_data7
```

##### Examing the new dataset

```{r}

boxplot(score ~ type_rank,
        data = anime_data7,
        main = "Score Distribution: Rank of Types",
        xlab = "Type Rank",
        ylab = "Anime Score",
        col = c("lightblue", "lightgreen","orange"))
anime_data7 <- anime_data7 |> select(-type)

```

#### Rating Processing

```{r}
anime_data8 <- anime_data7
anime_data8$rating_rank <- case_when(
  anime_data8$rating %in% c("R - 17+ (violence & profanity)", "PG-13 - Teens 13 or older") ~ "High",
  anime_data8$rating %in% c("PG - Children", "G - All Ages", "R+ - Mild Nudity") ~ "Mid",
  anime_data8$rating == "Rx - Hentai" ~ "Low",
  TRUE ~ NA_character_
)

anime_data8$rating_rank <- factor(anime_data8$rating_rank, levels = c("Low", "Mid", "High"))

anime_data8 <- anime_data8 |> select(-rating)
anime_data8
```

##### Examing the new dataset

```{r}
boxplot(score ~ rating_rank,
        data = anime_data8,
        main = "Score Distribution: Rank of Ratings",
        xlab = "Rating Rank",
        ylab = "Anime Score",
        col = c("lightblue", "lightgreen","orange"))
```

#### One-hot Encoding for Genres

```{r}
# One-hot encode only for the top genres
onehot_top10 <- anime_data8 |>
  mutate(row_id = row_number(),
         genres = str_split(genres, ",\\s*")) |>
  unnest(genres) |>
  filter(genres %in% top10_genre) |>
  mutate(dummy = 1) |>
  pivot_wider(
    id_cols = row_id,
    names_from = genres,
    values_from = dummy,
    values_fill = list(dummy = 0)
  )

# Join back to original data
data_1hot <- anime_data8 |>
  mutate(row_id = row_number()) |>
  left_join(onehot_top10, by = "row_id") |>
  select(-row_id)
# we delete the original genres column
data_1hot <- data_1hot |> select(-genres)
summary(data_1hot)
```

#### Last data processing for predictive analysis

Remove mal_id and title. Then, change status to factor modified_data will be the data we use for predictive analysis

```{r}
modified_data <- data_1hot
modified_data <- modified_data |> select(-mal_id)
modified_data <- modified_data |> select(-title)
modified_data$status <- as.factor(modified_data$status)
modified_data
```
